Drivers of sex differences in consumption

### 2017-07-05 sex-difference/sex-medicare-display.Rmd
sex medicare split complete

```{r consumption_by_age_and_sex}
read_tsv('data/tbl_consumption_age_sex.tsv') %>%
  ggplot(aes(x=factor(age), y=n, color=is_female)) +
  geom_boxplot()
```

>>>>

```{r consumption_by_age_and_sex}
read_tsv('data/tbl_consumption_age_sex.tsv') %>%
  mutate(y=total_n_claims, ci=1.96*sem_n_claims, ymin=y-ci, ymax=y+ci) %>%
  ggplot(aes(x=age, y=total_n_claims, ymin=ymin, ymax=ymax, color=sex)) +
  geom_point() + geom_linerange()
```
